% !TEX TS-program = pdflatex
% !TEX root = ../ArsClassica.tex

%*******************************************************
% Acknowledgements
%*******************************************************
\pdfbookmark{Acknowledgements}{Acknowledgements}

\chapter*{Acknowledgements}

\begin{flushright}
{\itshape
Astronomy compels the soul to look upwards \\and leads us from this world to another.}

\vspace{0.5em}
--- Plato
\end{flushright}

First and foremost I'd like to thank my supervisor, Sascha Quanz, for providing me with the guidance and resources with which to pursue this project.
You have been an inspiration, and my experience here at ETH has set me down an exciting path in exoplanet research.
It has been an honour to be a part of the growth of your group for the last two years, and I look forward to working with you in the future.

I have to thank the rest of the Exoplanet and Habitability Group for accepting me and teaching me over the last few years. 
Bibiana, thank you for our coffee discussions and your editing of this manuscript, I can't wait to see where you will go next.
To Judit Szulagyi, I cannot thank you enough for your constant support and mentorship, both in and outside of academia. 
Your advice has helped shape the course of my future, and I will always be grateful for that.
I'd especially like to  thank Gabrielle Cugno for always answering my questions, Eleonara Alei for our discussions of atmospheres and music and Adrian Glauser for getting me started at ETH and involved with this project.
And to all the rest: Anna, Franziska, Greta, Haiyang, Hans-Martin, Jie, Natalia, Silvan, Timothy and Tomas, thank you for our discussions, literature meetings, lessons and laughter. 
It has been a true pleasure to be a part of this group, I will miss it.

Additional thanks to Paul Molli\`{e}re for our discussions of petitRADTRANS and atmospheric retrievals, and for encouraging me to continue in my work.
I would have been lost multiple times throughout this project without your insight.

I must also thank my Zurich friends, without you it would have been impossible to survive here.
You have all made this a truly memorable experience.
Special thanks to Francisco, Rea and Hazal for proofreading this document.
Of course I have to thank my parents, Bill and Sherry, for supporting me in every possible way: not just here in Zurich, but throughout my life. 
I am eternally grateful for your love and encouragement.

Last, and certainly not least, I have to thank Polychronis Patapis for his supervision of this project. 
You got me into this and have set me on a path that I am excited to explore.
I can't imagine many others answering my constant questions late at night, and for pushing me to always do better. 
I'm so grateful to call you not just my supervisor, but my friend. 
There will always be coffee waiting for you whenever you come to visit.

\bigskip
\bigskip
